Reanalysis Step 4: Main Effects Outcome Analysis

### 2025-08-28 reanalysis-1-data_preparation.qmd
refactor

```{r setup}
#| include: false
source("dependencies.R")
setup_analysis(seed = 2025)
```

@@

```{r missing-assessment}
# Variables used in propensity score model
ps_model_vars <- c(
  "ever_lapse_binary",
  "baseline_VA_logMAR",
  "gender_cat",
  "race_ethnic_cat", 
  "insurance_cat",
  "age_cat",
  "CCI",
  "DCSI",
  "other_inject",
  "anti_VEGF",
  "focal_laser_flag",
  "PRP_flag",
  "glaucoma_bef_hitplus_cat",  # Missing coded as 0 (no condition)
  "otherretina_bef_hitplus_cat",  # Missing coded as 0 (no condition)
  "catsurg_before_hitplus_cat"
)

@@

variable_lists <- list(
  ps_model_vars = ps_model_vars,
  outcome_model_vars = outcome_model_vars,
  dr_vars = dr_vars,
  all_analysis_vars = all_analysis_vars,
  temporal_vars = c("cohort_id", "intermediate_VA_logMAR", "outcome_VA_logMAR", "baseline_VA_logMAR")
)
saveRDS(variable_lists, file.path(reanalysis_data_dir, "variable_lists.rds"))

>>>>

```{r setup}
#| include: false
source("dependencies.R")
source("functions.R")  # Load formula definitions and helper functions
setup_analysis(seed = 2025)
```

@@

```{r missing-assessment}
# Get variable lists from functions.R
reanalysis_vars <- get_reanalysis_variables()

# Variables used in propensity score model (standard version)
ps_model_vars <- reanalysis_vars$ps_model_vars

@@

# Use centralized variable lists from functions.R
variable_lists <- reanalysis_vars
variable_lists$outcome_model_vars <- outcome_model_vars
variable_lists$all_analysis_vars <- all_analysis_vars

saveRDS(variable_lists, file.path(reanalysis_data_dir, "variable_lists.rds"))

### 2025-08-28 reanalysis-3-propensity_scores.qmd
refactor

# Create enhanced formula including person_dr and treatment interactions
ps_formula_enhanced <- as.formula("ever_lapse_binary ~ 
  baseline_VA_logMAR +
  gender_cat +
  race_ethnic_cat +
  insurance_cat +
  age_cat +
  CCI +
  DCSI +
  other_inject +
  anti_VEGF +
  focal_laser_flag +
  PRP_flag +
  glaucoma_bef_hitplus_cat +
  otherretina_bef_hitplus_cat +
  catsurg_before_hitplus_cat +
  person_dr
")

@@

**Propensity score formula:**
```{r print-formula}
print(ps_formula_enhanced)

# Alternative: Use the standard formula from functions.R
ps_formula_standard <- get_matching_formula()

# For this analysis, we'll use the enhanced formula
ps_formula <- ps_formula_enhanced
```

>>>>

# Load functions with formula definitions
source("functions.R")

# Get the enhanced formula for reanalysis (includes dr_severity)
ps_formula_enhanced <- get_matching_formula_reanalysis()

@@

**Propensity score formula:**
```{r print-formula}
# Show the formula being used
print(ps_formula_enhanced)

# Set the formula to use for analysis
ps_formula <- ps_formula_enhanced
```

### 2025-08-28 reanalysis-4-outcome_analysis.qmd
refactor

```{r setup}
#| include: false
source("dependencies.R")
setup_analysis(seed = 2025)

@@

```{r define-formula}
# Load the standard formulas from functions.R
source("functions.R")

# Get the standard analysis formulas used in the original analysis
standard_formulas <- get_analysis_formulas()

# For reference, the original full formula is:
# standard_formulas$full

# For the reanalysis, we extend the full formula by adding:
# - dr_severity: diabetic retinopathy severity (No_DR, NPDR, PDR)
# - any_treatment: whether patient received any DR treatment
# These are new covariates not in the original analysis
main_effects_formula <- as.formula("outcome_va_vi_binary ~ 
  ever_lapse_binary + 
  dr_severity +
  any_treatment +
  baseline_VA_logMAR +
  gender_cat +
  race_ethnic_cat +
  insurance_cat +
  age_cat +
  CCI +
  DCSI +
  other_inject +
  anti_VEGF +
  focal_laser_flag +
  PRP_flag +
  glaucoma_bef_hitplus_cat +
  otherretina_bef_hitplus_cat +
  catsurg_before_hitplus_cat")
```

@@

  for (i in 1:n_imputations) {
    # Get dataset and weights
    imp_data <- imputed_datasets[[i]]
    imp_data$weights <- twang_weights[[i]]

@@

  for (i in 1:n_imputations) {
    imp_data <- imputed_datasets[[i]]
    imp_data$weights <- twang_weights[[i]]

>>>>

```{r setup}
#| include: false
source("dependencies.R")
source("functions.R")  # Load formula definitions and helper functions
setup_analysis(seed = 2025)

@@

```{r define-formula}
# Get the enhanced formulas for reanalysis from functions.R
reanalysis_formulas <- get_analysis_formulas_reanalysis()

# Use the full formula for main effects analysis
main_effects_formula <- reanalysis_formulas$full
```

@@

  # Initialize progress tracking
  progress <- init_progress(n_imputations, "Fitting models to imputed datasets")

  for (i in 1:n_imputations) {
    # Update progress
    progress <- update_progress(progress)

    # Get dataset and weights
    imp_data <- imputed_datasets[[i]]
    imp_data$weights <- twang_weights[[i]]

@@

  # Initialize progress tracking
  progress <- init_progress(n_imputations, "Calculating AMEs")

  for (i in 1:n_imputations) {
    # Update progress
    progress <- update_progress(progress)

    imp_data <- imputed_datasets[[i]]
    imp_data$weights <- twang_weights[[i]]
